\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-12-29 paper/mswp2012-proposal.tex
Add security introduction

\note{
\begin{itemize}
\item {\em Length: 1-2 pages}
\item Provide a brief explanation of the ethical issue involved and how it will be dealt with appropriately.
\item Are there any security-sensitive issues that apply to your proposal?
\end{itemize}
}

>>>>

%\note{
%\begin{itemize}
%\item {\em Length: 1-2 pages}
%\item Provide a brief explanation of the ethical issue involved and how it will be dealt with appropriately.
%\item Are there any security-sensitive issues that apply to your proposal?
%\end{itemize}
%}

Whenever personal data is stored in a centralized system discussions about security and privacy arise - this is especially true for sensible data like illnesses. Since the modern health care system deals with very sensible and personal data, security and privacy are two very important issue to deal with and we need to take the seriously.

By combining data from various sources the modern health care system is able to create a detailed health report of each and every participant and we need to make sure that these reports are anonymized and secured against attacks.
